\documentclass[letterpaper]{cvitae}
\begin{document}

% TITLE SECTION
\namesection{Antonio Chay}{
  {antonio@chay.cl} | 404 643 6661 \\
  {http://www.chay.cl}
}

% LEFT COLUMN
\begin{minipage}[t]{0.33\textwidth}

% Profile
\section{Profile}

\location{Efficient professional with more than 20 years of experience in development,
  support and deployments at different companies and countries}
%*responsible
%*commitment
%*focused on the company and the team
%*trust able ?, because I'm there

\textbullet{} Innovative and self motivated
\textbullet{} Self taught
\textbullet{} Quick to adapt and learn
\textbullet{} Team builder
\textbullet{} Technical leader
\textbullet{} Training and tutoring skills
\textbullet{} Rational, proactive and dedicated
\location{Spanish (native) \textbullet{} English \textbullet{} Portuguese}
\sectionspace
%----------------------------------------------------------------------------------------
\section {Skills}

\location{Expert knowledge of Unix systems}
\textbullet{} Solaris \textbullet{} Linux \textbullet{} OSF1 \textbullet{} HP-UX \textbullet{} Others

\location{Solid knowledge in different programming languages}
\textbullet{} C/C++ \textbullet{} Python \textbullet{} SQL \textbullet{} Perl \textbullet{} Unix scripting
\textbullet{} {Lisp \& Scheme} \textbullet{} Others

\location{Experience with several RDBMS}
\textbullet{} Oracle \textbullet{} PosgreSQL \textbullet{} MySQL \textbullet{} SQLite \textbullet{} Others

\location{Geographical Information Systems (GIS)}
\textbullet{} PostGIS \textbullet{} GDAL \textbullet{} Geos \textbullet{} KML \textbullet{} etc

\location{Unix toolbox}
\textbullet{} Grep \textbullet{} Sed \textbullet{} find \textbullet{} AWK \textbullet{} Make
\textbullet{} Vi \textbullet{} IPC \textbullet{} POSIX Threads \textbullet{} TCP/IP \textbullet{} etc

\location{Several VCS} \textbullet{} GIT \textbullet{} SVN \textbullet{} CVS \textbullet{}

\location{Wide acquaintance with cellular technologies}
\textbullet{} GSM \textbullet{} CDMA \textbullet{} Roaming \textbullet{} billing systems

\location{Decode/Encode MPEG4 format}

\location{High Throughput Computing}

\location{Linux Virtual Server (clustering)}

\location{Software analysis, profiling and design}

\location{Multi platform and multi technology integration}

\location{Agile Methodologies (Scrum, Kanban)}

\location{Customer support}

\sectionspace

\section{Education}
\location{Universidad Técnica Federico Santa María}
1992 - 1996 | Ingeniería de Ejecución en Informatíca
\end{minipage} % Left column ends here
%--- RIGHT COLUMN -----------------------------------------------------------------------
\begin{minipage}[t]{0.66\textwidth}
\section{Experience}
%----------------------------------------------------------------------------------------
\company{Pindrop}
\descript{| Staff Engineer}

\location{2015 – | Atlanta, Georgia - US}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Phone authentication and fraud detection.
\item Appliance build and setup. System Software team (back-end).
\item Python, C, Ruby, Bash scripting, MySQL, RHEL, Kickstart/Anaconda
\end{tightitemize}

\sectionspace
%----------------------------------------------------------------------------------------
\company{AirSage Inc.}
\descript{| Sr R\&D Software Engineer}

\location{2011 – 2015 | Atlanta, Georgia - US}
\begin{tightitemize}
\item Vehicle Traffic, GIS, GIS Database (PostGIS).
\item Python, IPCs, Linux, Linux Virtual Server, HTCondor (High throughput computing).
\item Postgres with PostGIS, GFS2
\end{tightitemize}

\sectionspace
%------------------------------------------------
\company{ISC S.A.}
\descript{| Ingeniero de Infraestructura}

\location{2010 – 2011 | Santiago - Chile}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Linux, LDAP, Cloud Services (massive virtual disk and email for 90K customers)
\item NetApp, Virtualization (KVM \& VMWare), Perl, Python
\end{tightitemize}

\sectionspace
%------------------------------------------------

\company{Wise Ocean Systems}
\descript{| Sr Software Engineer}

\location{2007 – 2010 | Valparaíso - Chile}
\begin{tightitemize}
\item Vehicle Traffic, Routing, GIS, GIS Database (PostGIS)
\item C++, Python, Perl, CORBA, IPCs, Hadoop, Google KML, Linux
\item Training and mentoring.
\end{tightitemize}

\sectionspace
%------------------------------------------------

\company{ITS S.A.}
\descript{| Analista Consultor}

\location{2002 – 2006 | Santiago - Chile, D.F. Mexico, Bogotá - Colombia, Quito - Ecuador}
\begin{tightitemize}
\item Integration with legacy Roaming system (CDMA - CIBER).
\item Roaming System backend development (C, C++, Perl, Oracle, Solaris, GSM, TAP3.X).
\item Part of the team for data/customer migrations in Mexico \& Colombia.
\end{tightitemize}

\sectionspace
%------------------------------------------------

\company{Comercial Voicenet Speech ltda}
\descript{| Software Engineer}

\location{2001 – 2002 | Santiago - Chile}
\begin{tightitemize}
\item Voice Recognition over the phone (voice commands).
\item Windows, C++, ISDN E1, Profiling, Win-Threads, embedded Perl.
\end{tightitemize}

\sectionspace
%------------------------------------------------

\company{H2M}
\descript{| Analista Senior}

\location{1999 - 2000 | Rio de Janeiro - Brazil}
\begin{tightitemize}
\item Outsourcing contract for \textbf{\textit{Sonda Brasil}} and \textbf{\textit{Telefônica Celular}}.
\item UI for customer attention (Visual Basic), back-end infrastructure (C \& C++), Ingres 6.4 (RDBMS), OSF1 (DEC Alpha), pthreads, TCP/IP, Index creation on text files (historic backup data)
\end{tightitemize}

\sectionspace
%------------------------------------------------

\company{Solartronix inc}
\descript{| Programmer}

\location{1998 – 1999 | Viña del Mar - Chile}
\begin{tightitemize}
\item Industrial automation solutions for concrete plants (CW6).
\item C Windows programming - Serial driver for communications between CW6 and personal computers.
\item Windows UI for the customer using the data (MS Access).
\item Analysis, installation and setup for the new development environment (Apple II to Mac OS Classic v9).
\end{tightitemize}

\sectionspace
%------------------------------------------------


\end{minipage} % end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}
